FATE summary results

### 2019-09-12 paper draft.Rmd
Tweaked short TS plot

```{r, echo=F}
GOA.ich <- readRDS("/Users/MikeLitzow 1/Documents/R/Fate/fate-ewi/GOA_ich_7.19.18.one.trend.rds") 
GOA.ich$summary
```

@@

plot.c <- ggplot(mod, aes(x=SST)) +
  theme_bw() +
  geom_density(fill=cb[3]) + 
  geom_hline(yintercept=0) + 
  geom_vline(xintercept = 0, lty=2) + 
  xlab("Slope") + 
  ylab("Density") +
  ggtitle(("c) Ichthyoplankton slope on SST")) +
  theme(title=element_text(size=8))

@@

```{r, echo=F}
GOA.zoop <- readRDS("/Users/MikeLitzow 1/Documents/R/Fate/fate-ewi/GOA_zoop_7.19.18.one.trend.rds") 
GOA.zoop$summary
```

>>>>

```{r, echo=F}
GOA.ich <- readRDS("/Users/MikeLitzow/Documents/R/Fate/fate-ewi/GOA_ich_7.19.18.one.trend.rds") 
GOA.ich$summary
```

@@

plot.c <- ggplot(mod, aes(x=SST)) +
  theme_bw() +
  geom_density(fill=cb[3]) + 
  geom_hline(yintercept=0) + 
  geom_vline(xintercept = 0, lty=2) + 
  xlab("Slope") + 
  ylab("Density") +
  ggtitle(("c) Ichthyo. slope on SST")) +
  theme(title=element_text(size=8))

@@

```{r, echo=F}
GOA.zoop <- readRDS("/Users/MikeLitzow/Documents/R/Fate/fate-ewi/GOA_zoop_7.19.18.one.trend.rds") 
GOA.zoop$summary
```
